---
title: "Curriculum Vitae"
author:
  - name: Christopher Chizinski
    url: https://humandimensions.unl.edu
    email: cchizinski2@unl.edu
    affiliations:
      - name: University of Nebraska-Lincoln
        department: School of Natural Resources
        address: "Lincoln, NE"
format:
  pdf:
    documentclass: awesome-cv
    template: custom
    keep-tex: true
    pdf-engine: xelatex
    cite-method: biblatex
    filters:
      - lua/multiple-bibliographies.lua
    include-in-header: preamble.tex
  html:
    toc: true
    toc-depth: 2
    theme: cosmo
    embed-resources: true
name: Christopher
surname: Chizinski
position: "Associate Professor of Human Dimensions"
address: "School of Natural Resources, University of Nebraska-Lincoln"
phone: "+1 402 471 1736"
www: humandimensions.unl.edu
email: "cchizinski2@unl.edu"
github: chrischizinski
linkedin: chrischizinski
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: d00000
csl: "csl/apa7-cv-jy-edition.csl"
execute:
  echo: false
  warning: false
  message: false
  cache: true
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(epoxy)
library(icons)

filter_year <- 2019

source("R/pull_citations.R")
source("R/pull_presentations.R")

current_year <- lubridate::year(lubridate::ymd(Sys.Date()))
```

# Education

```{r}
#| label: education

education_df <- read_csv(here::here("data", "education.csv")) %>%
  mutate(why_advisor = ifelse(do_thesis == 1, glue::glue("{str_to_title(num_advisor)}: {advisor}"), NA_character_))

education_df |>
  detailed_entries(what = institution,
                   when = year_end,
                   where = location,
                   with = degree,
                   why = c(thesis_title, why_advisor), .protect=TRUE)
```

\bigskip

# Professional appointments

```{r}
#| label: jobs

jobs_df <- read_csv(here::here("data", "prof_positions.csv"))

jobs_df |>
  detailed_entries(what = institution,
                   when = glue::glue("{start_year}--{end_year}"),
                   with = role,
                   where = location)
```

\newpage

# `r glue::glue("Grants awarded")`

```{r}
#| label: grants1

grants_df <- read_csv(here::here("data", "grants.csv"))

lifetime_amount <- scales::label_dollar()(sum(grants_df$amount))
reduced_amount <- scales::label_dollar()(grants_df |>
  filter(year >= filter_year) |> pull(amount) |> sum())
```

\medskip
- Grants awarded: `r glue::glue("{lifetime_amount} lifetime.")`
\medskip

```{r}
#| label: grants2

grants_df |>
  mutate(amount = scales::label_dollar()(amount),
         what = glue::glue("{authors}. {title}. {funder}. {amount} [{share}]")) |>
  brief_entries(what = what,
                   when = year)
```

\bigskip

# Student mentorship and advising

```{r}
#| label: students_load

grad_students_df <- read_csv(here::here("data", "students_advised.csv"))

grad_committees_df <- read_csv(here::here("data", "grad_committe_service.csv"))

undergrad_mentor_df <- read_csv(here::here("data", "undergrad_mentor.csv"))

state_pattern <- c("South Dakota|Nebraska|North Platte")

state_replace <- c("nebraska" = "Nebraska",
                   "south dakota" = "South Dakota",
                   "united states" = "United States",
                   "north platte" = "North Platte")
```

\medskip
## Postdoc and graduate student advising

```{r}
#| label: students_advise

grad_students_df |>
  arrange(desc(start)) |>
  filter(!is.na(name)) |>
  mutate(project = str_to_sentence(project),
          project = case_when(grepl(state_pattern, project,
                                 ignore.case = TRUE) ~str_replace_all(project, state_replace),
                              .default = project),
         what = glue::glue("{name}. [{position}]. {project}. {place}"),
         what = ifelse(!is.na(details), glue::glue("{what}. [{details}]"), what),
        ) |>
  detailed_entries(what = what,
                   when = glue::glue("{start}--{end}"))
```

\medskip
## Graduate student committee service

```{r}
#| label: students_committee

grad_committees_df |>
  arrange(desc(year)) |>
  filter(!is.na(name)) |>
  mutate(project = str_to_sentence(project),
          project = case_when(grepl(state_pattern, project,
                                 ignore.case = TRUE) ~str_replace_all(project, state_replace),
                              .default = project),
         what = glue::glue("{name}. [{position}]. {project}. {place}")) |>
  detailed_entries(what = what,
                   when = glue::glue("{year}"))
```

\medskip
## Undergraduate student mentorship

```{r}
#| label: undergrad

undergrad_mentor_df |>
  arrange(desc(year)) |>
  filter(!is.na(name)) |>
  mutate(what = glue::glue("{name}. {title}. [{project}]")) |>
  detailed_entries(what = what,
                   when = glue::glue("{year}"))
```

\newpage

# Publications

```{r}
#| label: scholar_information

scholar_data <- read_rds(here::here('data', 'scholar.rds'))
```

## Metrics
- Peer-reviewed publications: `r scholar_data$results[1]`
- Citation history: `r scholar_data$results[2]`
- `r icon_style(icons::academicons('google-scholar'), scale = 1.5)` H-index: `r scholar_data$results[3]`

\medskip

## `r glue::glue("Peer-reviewed manuscripts")`

```{r}
#| label: peerreview_pubs

bibliography_entries("bib/chizinski_pubs.bib")
```

## Books and book chapters

```{r}
#| label: chapter_pubs

bibliography_entries("bib/book_chapters.bib")
```

\bigskip

# Presentations

```{r}
#| label: presentation_information

presentation_data <- read_rds(here::here('data', 'presentation_numbers.rds'))
```

## Metrics
- Presentations: `r presentation_data$results[1]`

\medskip
## Invited presentations

```{r}
#| label: invited_presentations

bibliography_entries("bib/invited_presentations.bib")
```

\medskip

## `r glue::glue("Contributed presentations")`

```{r}
#| label: contributed_presentations

bibliography_entries("bib/contributed_presentations.bib")
```

\bigskip

# Honors and awards

```{r}
#| label: honors

honors_data <- read_csv(here::here('data', 'honors_awards.csv'))

honors_data |>
  arrange(desc(when)) |>
  detailed_entries(what = where,
                with = what,
                when = when)
```

\bigskip

# Teaching
## Regularly taught courses

```{r}
#| label: classes

courses_data <- read_csv(here::here('data', 'classes_taught.csv'))

courses_data |>
  pivot_longer(`2016`:last_col(), names_to = "year", values_to = "enrollment") |>
  mutate(year = as.numeric(year)) |>
    arrange(class_number, class_title) |>
  filter(!is.na(enrollment)) |>
  group_by(class_number, class_title) |>
  summarize(last_year_taught = last(year),
            enrollment_last_taught = last(enrollment)) |>
  ungroup() |>
  left_join(courses_data |> select(class_number:description),
            join_by("class_number","class_title")) |>
  detailed_entries(what = glue::glue("{class_title} ({class_number})"),
                when = glue::glue("{when_taught} semesters"),
                why = c(glue::glue("Last year taught: {last_year_taught}"),
                        glue::glue("Enrollment last taught: {enrollment_last_taught}"),
                        glue::glue("Description: {description}")))
```

## Other courses taught

- Applied Multivariate Analysis using R (NRES 898)
- Ecological Detective: Confronting Models with Data (NRES 898)
- Experimental Design and Analysis (NRES 898)
- Fisheries Science (NRES 463/898)
- Ecological Theory (NRES 898)
- Introduction to Agriculture and Natural Resources (NRES/AGRI 103)
- Introduction to Freshwater Ecology (RWFM 2305)

\bigskip
## Workshops and short courses

```{r}
#| label: workshops

workshops_data <- read_csv(here::here('data', 'workshops_other_training.csv'))

workshops_data |>
  arrange(desc(year)) |>
  mutate(title = str_trim(title),
         tile = str_to_title(title)) |>
  detailed_entries(what = glue::glue("{title} [{role}]. {location}"),
                   when = glue::glue("{date}"),
                   why = details)
```

# Service

\medskip

## Review and editorial service

```{r}
#| label: editorial

journal_data <- read_csv(here::here('data', 'journal_service.csv'))

journal_data |>
  arrange(desc(end)) |>
  detailed_entries(what = journal,
                   with = glue::glue("{role}"),
                   when = glue::glue("{start}--{end}"))
```

\medskip

## Journal Reviewer

```{r}
#| label: journal_review

c('Biological Invasions','Canadian Journal of Fisheries and Aquatic Sciences','Ecology of Freshwater Fish','Ecological Economics','Ecological Applications','Environmental Challenges','Fisheries Research','Fishery Bulletin','Forest Ecology and Management','Hydrobiologia','Ichthyological Research','Journal of Field Ornithology','Journal of Outdoor Recreation and Tourism','Journal of Wildlife Management','Human Dimensions of Wildlife','North American Journal of Fisheries Management','Marine and Coastal Fisheries','Marine Environmental Research','Oecologia','Oikos','Proceedings of the Southeastern Association of Fish and Game Agencies','Society and Natural Resources','Transactions of the American Fisheries Society','Wildlife Society Bulletin') -> journals_reviewed

journals_reviewed <- sort(unique(journals_reviewed))
```

`r glue::glue(" • {paste(journals_reviewed, collapse = ' • ')} •") `

\medskip

## External reviewer

```{r}
#| label: external_review

external_data <- read_csv(here::here('data', 'external_review.csv'))

external_data |>
  arrange(desc(year)) |>
  detailed_entries(what = with,
                   with = role,
                   when = year)
```

\medskip

## University service

```{r}
#| label: university_service

univ_service_data <- read_csv(here::here('data', 'university_service.csv'))

univ_service_data |>
  rowwise() |>
  mutate(order = as.numeric(str_remove_all(end, "[^0-9.-]")),
         order = ifelse(is.na(order), current_year, order),
         when = ifelse(!is.na(start), glue::glue("{start}--{end}"), end)) |>
  arrange(desc(order)) |>
  detailed_entries(what = with,
                   with = role,
                   when = when)
```
