---
title: "Curriculum Vitae"
author:
  - name: Christopher Chizinski
    url: https://humandimensions.unl.edu
    email: cchizinski2@unl.edu
    affiliations:
      - name: University of Nebraska-Lincoln
        department: School of Natural Resources
        address: "Lincoln, NE"
format:
  pdf:
    documentclass: awesome-cv
    keep-tex: true
    pdf-engine: xelatex
    filters:
      - lua/strong.lua
    include-in-header: preamble.tex
    include-before-body: header.tex
  html:
    toc: true
    toc-depth: 2
    theme: cosmo
    css: cv.css
    embed-resources: true
name: Christopher
surname: Chizinski
position: "Professor of Human Dimensions"
address: "School of Natural Resources, University of Nebraska-Lincoln"
phone: "+1 402 472 8136"
www: humandimensions.unl.edu
email: "cchizinski2@unl.edu"
github: chrischizinski
linkedin: chrischizinski
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: d00000
csl: "csl/apa7-cv-jy-edition.csl"
params:
  filter_year: 2020
title-block: false
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(rlang)

# Load custom CV formatting functions
source("R/functions.R")

filter_year <- params$filter_year

source("R/pull_citations.R")
source("R/pull_presentations.R")

current_year <- lubridate::year(lubridate::ymd(Sys.Date()))

header_lines <- c(
  "\\name{Christopher}{Chizinski}",
  "\\position{Professor of Human Dimensions}",
  "\\address{School of Natural Resources, University of Nebraska-Lincoln}",
  "\\mobile{402-472-8136}",
  "\\email{cchizinski2@unl.edu}",
  "\\homepage{humandimensions.unl.edu}",
  "\\github{chrischizinski}",
  "\\linkedin{chrischizinski}",
  "\\makecvheader",
  glue::glue("\\makecvfooter{{\\today}}{{Christopher Chizinski~~~\\textbar~~~Curriculum Vitae~~~\\textbar~~~Items since {filter_year}}}{{\\thepage}}")
)

writeLines(header_lines, "header.tex")
```

# Education

```{r}
#| label: education
#| results: asis

education_df <- read_csv(here::here("data", "education.csv")) %>%
  mutate(why_advisor = ifelse(do_thesis == 1, glue::glue("{str_to_title(num_advisor)}: {advisor}"), NA_character_),
         why = purrr::map2(thesis_title, why_advisor, ~c(.x, .y)))

cv_entries(education_df,
           what = institution,
           when = year_end,
           where = location,
           with = degree,
           why = why,
           .protect = FALSE)
```

\bigskip

# Professional appointments

```{r}
#| label: jobs
#| results: asis

jobs_df <- read_csv(here::here("data", "prof_positions.csv")) |>
  mutate(when = glue::glue("{start_year}--{end_year}"))

cv_entries(jobs_df,
           what = institution,
           when = when,
           with = role,
           where = location,
           .protect = FALSE)
```

# `r glue::glue("Grants awarded")`

```{r}
#| label: grants1

grants_df <- read_csv(here::here("data", "grants.csv"))

lifetime_amount <- gsub("\\$", "\\\\$", scales::label_dollar()(sum(grants_df$amount)))
reduced_amount <- gsub("\\$", "\\\\$", scales::label_dollar()(grants_df |>
  filter(year >= filter_year) |> pull(amount) |> sum()))
```

\medskip
- Grants awarded: `r glue::glue("{lifetime_amount} lifetime.")`
\medskip
\begingroup
\renewcommand*{\entrytitlestyle}[1]{{\fontsize{9pt}{1em}\bodyfontlight\upshape\color{black} #1}}
\renewcommand*{\entrypositionstyle}[1]{{\fontsize{9.5pt}{1em}\bodyfont\scshape\color{graytext} #1}}
\renewenvironment{cventries}{%
  \vspace{\acvSectionContentTopSkip}
  \begin{flushleft}
}{%
  \end{flushleft}
}

```{r}
#| label: grants2
#| results: asis

name_pattern <- "(Chizinski,\\s*C\\.?\\s*J\\.?|Chizinski,\\s*C\\.?J\\.?|Chizinski,\\s*C\\.?|Chizinski,\\s*CJ|C\\.?\\s*J\\.?\\s*Chizinski|C\\.?\\s*Chizinski|CJ\\s*Chizinski|Christopher\\s*Chizinski)"

grants_recent_df <- grants_df |>
  filter(year >= filter_year)

grants_recent_df |>
  mutate(amount = scales::label_dollar()(amount),
         amount = gsub("\\$", "\\\\$", amount),  # Escape $ for LaTeX
         share = gsub("%", "\\\\%", share),  # Escape % for LaTeX
         authors = str_replace_all(authors, regex(name_pattern), "\\\\textbf{\\1}"),
         main = title,
         why = purrr::pmap(list(authors, funder, amount, share), ~c(..1, ..2, glue::glue("{..3} [{..4}]"), "\\vspace{2mm}"))) |>
  cv_entries(what = "",
             with = main,
             when = year,
             why = why,
             .protect = FALSE)
```
\endgroup

\bigskip

# Student mentorship and advising

```{=latex}
\begingroup
\renewenvironment{cventries}{%
  \vspace{\acvSectionContentTopSkip}
  \begin{flushleft}
}{%
  \end{flushleft}
}
\renewcommand*{\cventry}[5]{%
  \hspace*{5mm}%
  \setlength\tabcolsep{0pt}%
  \setlength{\extrarowheight}{0pt}%
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} L{\textwidth - 4.5cm} R{4.5cm}}%
    \ifempty{#2#3}{\entrypositionstyle{#1} & \entrydatestyle{#4} \\}%
      {\entrytitlestyle{#2} & \entrylocationstyle{#3} \\%
      \entrypositionstyle{#1} & \entrydatestyle{#4} \\}%
    \multicolumn{2}{L{\textwidth}}{\descriptionstyle{#5}}%
  \end{tabular*}%
}
```

```{r}
#| label: students_load

grad_students_df <- read_csv(here::here("data", "students_advised.csv"))

grad_committees_df <- read_csv(here::here("data", "grad_committe_service.csv"))

undergrad_mentor_df <- read_csv(here::here("data", "undergrad_mentor.csv"))

state_pattern <- c("South Dakota|Nebraska|North Platte|Kansas River|North Central United States|Ducks Unlimited|Great Plains|Asian|California")

state_replace <- c("nebraska" = "Nebraska",
                   "south dakota" = "South Dakota",
                   "united states" = "United States",
                   "north platte" = "North Platte",
                   "kansas river" = "Kansas River",
                   "north central united states" = "North Central United States",
                   "ducks unlimited" = "Ducks Unlimited",
                   "great plains" = "Great Plains",
                   "asian" = "Asian",
                   "california" = "California")
```

\medskip
## Postdoc and graduate student advising

```{r}
#| label: students_advise
#| results: asis

grad_students_df |>
  arrange(desc(start)) |>
  filter(!is.na(name)) |>
  filter(start >= filter_year) |>
  mutate(project = str_to_sentence(project),
          project = case_when(grepl(state_pattern, project,
                                 ignore.case = TRUE) ~str_replace_all(project, state_replace),
                              .default = project),
         title = "",
         with = glue::glue("\\studentname{{{name}}}"),
         when = glue::glue("{start}--{end}"),
         why = purrr::map(purrr::pmap(list(position, project, place, details), ~c(..1, ..2, ..3, ..4)), ~{
           items <- .x
           items <- items[!is.na(items) & items != ""]
           c(items, "\\vspace{2mm}")
         })
        ) |>
  cv_entries(what = title,
             with = with,
             when = when,
             why = why,
             .protect = FALSE)
```

\medskip
## Graduate student committee service

```{r}
#| label: students_committee
#| results: asis

grad_committees_df |>
  arrange(desc(year)) |>
  filter(!is.na(name)) |>
  filter(year >= filter_year) |>
  mutate(project = str_to_sentence(project),
          project = case_when(grepl(state_pattern, project,
                                 ignore.case = TRUE) ~str_replace_all(project, state_replace),
                              .default = project),
         title = "",
         with = glue::glue("\\studentname{{{name}}}"),
         when = as.character(year),
         why = purrr::map(purrr::pmap(list(position, project, place, details), ~c(..1, ..2, ..3, ..4)), ~{
           items <- .x
           items <- items[!is.na(items) & items != ""]
           c(items, "\\vspace{2mm}")
         })) |>
  cv_entries(what = title,
             with = with,
             when = when,
             why = why,
             .protect = FALSE)
```

\medskip
## Undergraduate student mentorship

```{r}
#| label: undergrad
#| results: asis

undergrad_mentor_df |>
  arrange(desc(year)) |>
  filter(!is.na(name)) |>
  filter(year >= filter_year) |>
  mutate(title = "",
         with = glue::glue("\\studentname{{{name}}}"),
         when = as.character(year),
         why = purrr::map(purrr::pmap(list(title, project), ~c(..1, glue::glue("[{..2}]"))), ~{
           items <- .x
           items <- items[!is.na(items) & items != ""]
           c(items, "\\vspace{2mm}")
         })) |>
  cv_entries(what = title,
             with = with,
             when = when,
             why = why,
             .protect = FALSE)
```

```{=latex}
\endgroup
```

# Publications

```{r}
#| label: scholar_information

scholar_data <- read_rds(here::here('data', 'scholar.rds'))
```

## Metrics
- Peer-reviewed publications: `r scholar_data$results[1]`
- Citation history: `r scholar_data$results[2]`
- \aiGoogleScholar\ H-index: `r scholar_data$results[3]`

\medskip

## `r glue::glue("Peer-reviewed manuscripts")`

```{r}
#| label: peerreview_pubs
#| results: asis

cv_bibliography("bib/reduced_chizinski_pubs.bib")
```

## Books and book chapters

```{r}
#| label: chapter_pubs
#| results: asis

cv_bibliography("bib/book_chapters.bib")
```

\bigskip

# Presentations

```{r}
#| label: presentation_information

presentation_data <- read_rds(here::here('data', 'presentation_numbers.rds'))
```

## Metrics
- Presentations: `r presentation_data$results[1]`

\medskip
## Invited presentations

```{r}
#| label: invited_presentations
#| results: asis

cv_bibliography("bib/invited_presentations_reduced.bib")
```

\medskip

## `r glue::glue("Contributed presentations")`

```{r}
#| label: contributed_presentations
#| results: asis

cv_bibliography("bib/reduced_contributed_presentations.bib")
```

\bigskip

# Honors and awards

```{r}
#| label: honors
#| results: asis

honors_data <- read_csv(here::here('data', 'honors_awards.csv'))

honors_data |>
  arrange(desc(when)) |>
  filter(when >= filter_year) |>
  mutate(when = as.character(when),
         title = what,
         with = "",
         why = purrr::map(where, ~c(.x, "\\vspace{2mm}"))) |>
  cv_entries(what = title,
             with = with,
             when = when,
             why = why,
             .protect = FALSE)
```

\bigskip

# Teaching
## Regularly taught courses

```{r}
#| label: classes
#| results: asis

courses_data <- read_csv(here::here('data', 'classes_taught.csv'))

courses_data |>
  pivot_longer(`2016`:last_col(), names_to = "year", values_to = "enrollment") |>
  mutate(year = as.numeric(year)) |>
    arrange(class_number, class_title) |>
  filter(!is.na(enrollment)) |>
  group_by(class_number, class_title) |>
  summarize(last_year_taught = last(year),
            enrollment_last_taught = last(enrollment)) |>
  ungroup() |>
  left_join(courses_data |> select(class_number:description),
            join_by("class_number","class_title")) |>
  filter(last_year_taught >= filter_year) |>
  mutate(what = glue::glue("{class_title} ({class_number})"),
         when = glue::glue("{when_taught} semesters"),
         why = purrr::pmap(list(last_year_taught, enrollment_last_taught, description),
                           ~c(glue::glue("Last year taught: {..1}"),
                              glue::glue("Enrollment last taught: {..2}"),
                              glue::glue("Description: {..3}"),
                              "\\vspace{2mm}"))) |>
  cv_entries(what = what,
             when = when,
             why = why,
             .protect = FALSE)
```

## Other courses taught

- Applied Multivariate Analysis using R (NRES 898)
- Ecological Detective: Confronting Models with Data (NRES 898)
- Experimental Design and Analysis (NRES 898)
- Fisheries Science (NRES 463/898)
- Ecological Theory (NRES 898)
- Introduction to Agriculture and Natural Resources (NRES/AGRI 103)
- Introduction to Freshwater Ecology (RWFM 2305)

\bigskip
## Workshops and short courses

```{r}
#| label: workshops
#| results: asis

workshops_data <- read_csv(here::here('data', 'workshops_other_training.csv'))

workshops_data |>
  arrange(desc(year)) |>
  filter(year >= filter_year) |>
  mutate(title = str_trim(title),
         title = str_to_title(title),
         what = glue::glue("{title} [{role}]. {location}"),
         when = as.character(date),
         why = purrr::map(details, ~c(.x, "\\vspace{2mm}"))) |>
  cv_entries(what = what,
             when = when,
             why = why,
             .protect = FALSE)
```

# Service

\medskip

## Review and editorial service

```{r}
#| label: editorial
#| results: asis

journal_data <- read_csv(here::here('data', 'journal_service.csv'))

journal_data |>
  arrange(desc(end)) |>
  mutate(end_year = suppressWarnings(as.numeric(str_remove_all(end, "[^0-9]"))),
         end_year = ifelse(is.na(end_year), current_year, end_year),
         when = glue::glue("{start}--{end}")) |>
  filter(end_year >= filter_year) |>
  cv_entries(what = journal,
             with = role,
             when = when,
             .protect = FALSE)
```

\medskip

## Journal Reviewer

```{r}
#| label: journal_review

c('Biological Invasions','Canadian Journal of Fisheries and Aquatic Sciences','Ecology of Freshwater Fish','Ecological Economics','Ecological Applications','Environmental Challenges','Fisheries Research','Fishery Bulletin','Forest Ecology and Management','Hydrobiologia','Ichthyological Research','Journal of Field Ornithology','Journal of Outdoor Recreation and Tourism','Journal of Wildlife Management','Human Dimensions of Wildlife','North American Journal of Fisheries Management','Marine and Coastal Fisheries','Marine Environmental Research','Oecologia','Oikos','Proceedings of the Southeastern Association of Fish and Game Agencies','Society and Natural Resources','Transactions of the American Fisheries Society','Wildlife Society Bulletin') -> journals_reviewed

journals_reviewed <- sort(unique(journals_reviewed))
```

`r glue::glue(" • {paste(journals_reviewed, collapse = ' • ')} •") `

\medskip

## External reviewer

```{r}
#| label: external_review
#| results: asis

external_data <- read_csv(here::here('data', 'external_review.csv'))

external_data |>
  arrange(desc(year)) |>
  filter(year >= filter_year) |>
  mutate(when = as.character(year)) |>
  cv_entries(what = with,
             with = role,
             when = when,
             .protect = FALSE)
```

\medskip

## University service

```{r}
#| label: university_service
#| results: asis

univ_service_data <- read_csv(here::here('data', 'university_service.csv'))

univ_service_data |>
  rowwise() |>
  mutate(order = as.numeric(str_remove_all(end, "[^0-9.-]")),
         order = ifelse(is.na(order), current_year, order),
         when = ifelse(!is.na(start), glue::glue("{start}--{end}"), end)) |>
  arrange(desc(order)) |>
  filter(order >= filter_year) |>
  ungroup() |>
  cv_entries(what = with,
             with = role,
             when = when,
             .protect = FALSE)
```
